Dependently Typed Multi-stage Calculus

### 2019-11-20 slides/main.tex
Finished Hanada.

>>>>

\begin{frame}[fragile]{\LTP [Hanada\&Igarashi'14]}
    Multi-stage calculus with Cross Stage Persistence (CSP)
    \begin{block}{Terms}
    \begin{tabbing}
        \hspace{5mm} \( M \) \= \( ::= c \) \hspace{20mm} \= (constants) \\
        \> \( \mid \TB M \) \> (quote) \\
        \> \( \mid \TBL M \) \> (unquote) \\
        \> \( \mid \textbf{run}\ M \) \> (run) \\
        \> \( \mid \% M \) \> (CSP) \\
        \> \( \mid x \mid \lambda x:\tau.M \mid M\ M \) \\
    \end{tabbing}
    \end{block}
\end{frame}

\begin{frame}[fragile]{Types of \LTP}
    \begin{block}{Types}
    \begin{tabbing}
        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
        \> \( \mid \tau \to \tau \) \> (function type) \\
        \> \( \mid \TW\ \tau \) \> (code type)
        % \> \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
    \end{tabbing}
    \end{block}
   \note{
    }
\end{frame}

\begin{frame}[fragile]{Example of \LTP}
    \begin{table}
        \begin{tabular}{ c | c | c }
            & \LTP & MetaOCaml \\[2mm]
            \hline
            Make code & \( \textbf{let } a = \TB (1 + 2) \) & \verb| let a = .<(1+2)>.| \\[2mm]
            Embed code & \( (\TB (\TBL a + \TBL a)) \) & \verb| .<(.~a)+(.~a)>.| \\[2mm]
            Run code & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run .<(1+2)>.| \\[2mm]
            Code type & \( \TW\ \text{Int} \) & \verb| int code |
        \end{tabular}
    \end{table}
\end{frame}

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
\end{frame}

\begin{frame}[fragile]{Types of \LMD}
    \begin{block}{Types}
    \begin{tabbing}
        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
        \> \( \mid \tau \to \tau \) \> (function type) \\
        \> \( \mid \TW\ \tau \) \> (code type)
        % \> \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
    \end{tabbing}
    \end{block}
   \note{
    }
\end{frame}
